---
title: "QM_assignment_5"
output: pdf_document
date: "2022-11-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#In light of objective function and restrictions, such as employment levels and corporate revenues, the Emax corporation's goal is to maximize profit of new items.

#Libraries  for the current environment
```{r}
library(lpSolve)
library(lpSolveAPI)
library(goalprog)
```

#Where #P = total (discounted) profit over the life of the new products, the objective function #Maximize Z = P - 6C - 3D,
#C = Change (in either direction) in the level of employment at the moment, and #D = Decrease (if any) in earnings from the level of the present year in the following year.


#Each new product's lptable is displayed in the table.
```{r}
lp_table<- matrix(c("Total Profit", "Employment Level", "Earnings Next Year",
                       20,6,8,
                       15,4,7,
                       25,5,5,
                       "Maximize","=50",">=75",
                       "Millions of Dollars", "Hundreds of Employees", "Millions of Dollars"), ncol=6, byrow = F)
colnames(lp_table) <- c("Factor","Product 1", "Product 2", "Product 3", "Goal", "Units")
as.table(lp_table)
```

#Under goal programming, the objective functions were imported via a Lp file. The formulations utilized for the objective function and constraints to the lp formulation are as follows:

#Maximum objective function: 20x1, 15x2, and 25x3 - 6y1m, 6y1p, and 3y2m;

#Constraints
#6x1 + 4x2 + 5x3 + y1m - y1p = 50;
#8x1 + 7x2 + 5x3 + y2m - y2p = 75;

```{r}
getwd()
setwd("/Users/bharathreddy/Desktop")
lp<-read.lp("gp.lp")
lp
```

#Goal programming model 
```{r}
solve(lp)
```
#The result of the formulation of lp is 0, indicating success.

# Purposeful action to maximize profit.
```{r}
get.objective(lp)
```

#Variable value of goal programming model
```{r}
get.variables(lp)
```

#interpretation
#1. From above, it is evident that X3 has undergone a metamorphosis. The only product that the company can create, 15 units of Product 3, is the one that will maximize profit.

#2.The firm's employment levels were exceeded by 25 hundred employees despite the fact that the maximum number of employees was 50 hundred, as per the restrictions outlined above.

#3. The intention of Y2P and Y2M was to detect any variances in earnings for the next year. According to the formulation above, it exhibited no deviations.

#4. The company is maximizing a 225 million dollar profit.
